\vspace{-2cm} Government websites as data: \\ A methodological pipeline with application to the websites of municipalities in the United States

### 2019-08-02 paper/manuscript_psrmNote.tex
made remaining revisions

@@

We illustrate the analysis of municipal website content by studying differences in website content based on the party of the mayor. As we reviewed above, the partisanship of the mayor has been found in past research to affect several features of city governance. However, \citet{gerber2011mayors} note that, due to the constraints of state and national policies, municipalities lack discretion in many domains of governance. These constraints do not apply to website contents. City governments have great discretion in composing their websites, modifying website content is low cost relative to other policy changes, and, as reviewed above, city websites provide an effective and often-used means of communication with city residents.

>>>>

Our research objectives and corresponding contributions are two-fold. First, we present a set of tools that can be effectively used in combination to automatically gather sections of substantive plain text from government websites---covering entire contents including the plain HTML files, and linked files in various formats (e.g., DOC, PDF, and TXT). Our pipeline provides researchers with a highly scalable approach to constructing comprehensive samples of textual data associated with government entities.\footnote{It is useful to note a couple of features that we do not intend to provide with this pipeline. First, this is not intended to be a pipeline for scraping and analyzing any and all websites. Our focus is on government websites, as we assume that the contents are in the public domain, and not subject to limitations on the application of scraping technology. Second, though such extensions would be valuable, we do not address the collection and analysis of image, video, sound, and  tabular data from government websites.} Second, we gather and analyze a dataset that covers the textual contents of websites from over two hundred municipal governments in the United States. By studying the covariation of topical contents on these websites with the partisanship of the city mayors, we validate the utility of both the pipeline, and this specific dataset. In summary, our contributions offer scholars of government a roadmap for collecting, and an example of, large scale textual data extracted from government websites.

@@

City mayors use government websites to present their policy priorities to the public. Consider an example; \cite[p.55]{formicola2003faith} document a significant website content change during a transition in mayoral administrations in the city of Indianapolis. Under the Republican mayor Stephen Goldsmith, voluminous content was added to the city website in connection with the Front Porch Alliance---a faith-based initiative to create partnerships with religious organizations for the use and administration of city resources. Faith-based initiatives represent a type of public-private partnership that is popular with Republicans \citep{saperstein2003public}. When Democrat Bart Peterson took office in 2000, the material related to the Front Porch Alliance was removed from the website. We consider whether the partisan manipulation of city website contents documented in this example holds in a large-scale and more recent sample of city websites. We illustrate the analysis of municipal website content by studying the ways in which differences in website content correlate with the partisanship of the city's mayor mayor. As we reviewed above, the partisanship of the mayor has been found in past research to affect several features of city governance. However, \citet{gerber2011mayors} note that, due to the constraints of state and national policies, municipalities lack discretion in many domains of governance. These constraints do not apply to website contents. City governments have great discretion in composing their websites, modifying website content is low cost relative to other policy changes, and, as reviewed above, city websites provide an effective and often-used means of communication with city residents.
